---
title: "Using RadialGO"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, results='hide'}
library(radialgo)
install.packages("BiocManager", repos="http://cran.utstat.utoronto.ca/")
library(BiocManager)
BiocManager::install("topGO")
BiocManager::install("hgu95av2.db")
BiocManager::install("ALL")
library(topGO)
library(ALL)
```
# Introduction
RadialGO is a package for visualizing Gene Ontology enrichment analyses, using a 
radial tree layout. This document gives a quick tour of how to use the package. 

# GO Enrichment
The function generateGraph() produces a graph of the GO enrichment, taking as 
input 3 parameters: the first is a CSV file containing a "GO ID" column, which 
consists of Gene Ontology identifiers such as "GO:0008150", and a "P value" 
column, consisting of the corresponding P-value in the enrichment analysis. 

An example workflow follows. 

# Example

For this example we will obtain the GO enrichment results using the topGO package.
```{r, include=TRUE, , results='hide', message=FALSE}
data(ALL)
data(geneList)
affyLib <- paste(annotation(ALL), "db", sep = ".")
library(package = affyLib, character.only = TRUE)
sampleGOdata <- new("topGOdata", description = "Simple session", ontology = "BP",
                    allGenes = geneList, geneSel = topDiffGenes, nodeSize = 10, 
                    annot = annFUN.db, affyLib = affyLib)
resultFisher <- runTest(sampleGOdata, algorithm = "classic", statistic = "fisher")
```
This gets us our GO enrichment analysis results in the variable resultFisher.
We can use the score() function to extract a named numeric vector containing GO IDs
and P values, which we will use to build a data frame.

```{r, include=TRUE, results='hide'}
df <- data.frame("GO ID"= names(score(resultFisher)), "P value"= as.numeric(score(resultFisher)))
df
```

We can store this data frame easily using the following code:
```{r, include=TRUE}
write.csv(df, "enrichment_results.csv")
```

Once we have this data frame, we can call generateGraph() to create our graph, 
and then render it: 

```{r, include=TRUE}
library(radialgo)
library(DiagrammeR)
gr <- generateGraph(df, 5, 0.5)
DiagrammeR::grViz(generate_dot(gr))
```
